A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
cite here package closes #46

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

@@

This command will create a file with the name `README.Rmd`.
<!--knit/rmarkdown will be explained in section above-->
When you knit this file, it, in turn, creates a `README.md`.
That means you can include R code or plots etc., within the readme.
The `README.md` file will look pleasant in the browser on `r link("https://github.com/aaronpeikert/repro-tutorial#readme", "GitHub")`.

>>>>

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
We recomend the [`here`](https://github.com/r-lib/here)[^here] package [@R-here] to refer to files, because it works consistently across different operating systems, and between R scripts and [R Markdown].
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

[^here]: https://github.com/r-lib/here

@@

This command will create a file with the name `README.Rmd`.
<!--knit/rmarkdown will be explained in section above-->
When you knit this file, it, in turn, creates a `README.md`.
That means you can include R code or plots etc., within the readme.
The `README.md` file will look pleasant in the browser on [GitHub](https://github.com/aaronpeikert/repro-tutorial#readme).
